---
title: "Distributions in R"
author: "MTH225"
date: "August 29, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Gaussian or normal distribution (suffix is 'norm')

### Find the following probabilities:

* The probability that a standard normal random variable assumes a value less than 1.5
* The probability that a normal random variable with mu=100 and sigma=15 assumes a value greater than 120
* The probability that a normal random variable with mu=500 and sigma=100 assumes a value between 450 and 550.

```{r gaussian, echo=TRUE}
# R code goes here
```

## The t distribution (suffix is 't')

### Find the following probabilities:

* The probability that a t random variable with 15 degrees of freedom assumes a value less than 1.5
* The probability that a t random variable with 20 degrees of freedom assumes a value greater than 2
* The probability that a t random variable with 22 degrees of freedom assumes a value between -2 and 2.


```{r t, echo=TRUE}
# R code goes here
```


## The chi-square distribution (suffix is 'chisq')

### Find the following probabilities:

* The probability that a chi-square random variable with 15 degrees of freedom assumes a value greater than 20
* The probability that a chi-square random variable with 20 degrees of freedom assumes a value greater than 28
* The probability that a chi-square random variable with 22 degrees of freedom assumes a value greater than 25.


```{r chisquare, echo=TRUE}
# R code goes here
```
