---
title: "Week2_Ex1"
author: "Equinn"
date: "September 5, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Use the rbeta() function to generate a sample of 100 observations from a beta distribution with parameters shape1=1 and shape2=2.

Call the result y.

You can display the documentation for the rbeta() function by entering the command

?rbeta

in the Console window.

```{r step 1}
#
```

## Draw a histogram of the sample

Use the hist() function

```{r step 2}
#
```

## Show quantiles

Use the qbeta() function with the same parameters to find the 25th and 75th percentiles of a beta distribution with those parameters. 

```{r step 3}
#
```

## determine the quantiles for the sample

Use the quantiles() function to display the 25th and 75th percentiles of the sample.  Compare these numbers to the values returned by qbeta()

```{r step 4}
#
```

## determine the mean of the sample

Use the mean() function to display the mean of the sample.  Compare this to the theoretical mean of a beta distribution with the given parameters. (see the Wikipedia entry for 'beta distribution')

```{r step 5}
#
```